Well Hello There!

### 2024-05-09 index.qmd
Update
Update index.qmd

Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 2nd year, double majoring in Sociology and Communications & New Media!

@@

### SC3101 - Social Thought and Theory

@@

### HS1501 - Artificial Intelligence and Society

@@

### DTK1234 - Design Thinking

@@

Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms!

>>>>

Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 3rd year, double majoring in Sociology and Communications & New Media!

@@

### Social Thought and Theory

@@

### Artificial Intelligence and Society

@@

### Design Thinking

@@

Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms
